A full approximation scheme multilevel method \\ for nonlinear variational inequalities

### 2023-07-13 paper/fascd.tex
work on draft of discussion section

@@

FIXME smoother could be Newton semi-smooth \cite{BensonMunson2006}; smoother could be interior point method, etc.; smoother could use GMG or AMG on step equations but this is not seen to be necessary in applications so far

>>>>

FIXME So the difference between FAScd and \cite{GraeserKornhuber2009} are: (1) FAS coarse corrections, (2) no attempt to do monotone/truncated multigrid which would be a mess (I think) across the FE infrastructure, (3) clarity on what sets you can use in $V(\nu_1,\nu_2)$ cycles, with bigger up-smoother sets in particular, and most importantly (4) implementation within the mature Firedrake/PETSc library framework where one can easily hook up an active-set Newton step as a smoother.

FIXME main difference relative to monotone multigrid \cite{Kornhuber1994} and PFAS \cite{BrandtCryer1983} is that method is not tied to, or presented in terms of, an PNGS type smoother

FIXME at a high level one might say FAScd merely generates coarse VI problems which, once solved, make helpful admissible additions to the eventual V-cycle update; the method is smoother-agnostic; smoother could be Newton semi-smooth \cite{BensonMunson2006}, interior point method, etc.

FIXME VINewton smoother could use GMG or AMG on linear step equations, but this was not seen to be necessary in applications so far and was not even tested

@@
